### 2010-04-01 papers/icfp-2010-desc/paper_desc.tex
Desc@ICFP: s/sum-of-product/sum-of-products/

In ML-like languages, datatype definitions are called
\emph{sum-of-product}. A datatype is defined by a finite sum of
constructors, each composed by a product of arguments. To embrace
these datatypes, we need to capture this grammar.

With dependent types, the notion of sum-of-product translates into
\emph{sigmas-of-sigmas}. However, a direct encoding of datatypes
through raw $\Sigma$-types is not a viable option. Indeed, to program
with these datatypes, we need an induction principle. An encoding is
unable to deliver such
operation~\cite{geuvers:induction-not-derivable}.

@@

Again, this is a clear reminiscence of the sum-of-product style: we
have a finite sum of constructors. Every description can be expressed
in this style, using a singleton as a constructor if
necessary. Converselly, a tagged description can be turned into a
full-blown description. We denote $\toDesc{\V{TD}}$ the description
computed from the tagged description $\V{TD}$.

>>>>

In ML-like languages, datatypes are presented as a
\emph{sum-of-products}. A datatype is defined by a finite sum of
constructors, each composed by a product of arguments. To embrace
these datatypes, we need to capture this grammar.

With dependent types, the notion of sum-of-products translates into
\emph{sigmas-of-sigmas}. However, a direct encoding of datatypes
through raw $\Sigma$-types is not a viable option. Indeed, to program
with these datatypes, we need an induction principle. An encoding is
unable to deliver such
operation~\cite{geuvers:induction-not-derivable}.

@@

Again, this is a clear reminiscence of the sum-of-products style: we
have a finite sum of constructors. Every description can be expressed
in this style, using a singleton as a constructor if
necessary. Converselly, a tagged description can be turned into a
full-blown description. We denote $\toDesc{\V{TD}}$ the description
computed from the tagged description $\V{TD}$.
